video-and-reproducible-science

### 2016-03-27 nyu-data-science-reproducibility-16/video-reproducibility.Rmd
Edit reproducible science slide

## Reproducibility in Psychological Science

## Data Sharing Sharpens Focus on Substance

@@

<div class="centered">
<a href="http://doi.org/10.1126/science.1093567">
<img src="img/deloache.science.jpg" height=500px>

[[@deloache_scale_2004]](http://doi.org/10.1126/science.1093567)
</a>
</div>

>>>>

## Is Psychological Science Reproducible?

<div class="centered">
<a href="http://cos.io">
<img src="https://cos.io/static/img/icons/cos_wide.png">
</div>
</a>

- Nosek et al., [[@collaboration_estimating_2015]](http://doi.org/10.1126/science.aac4716)
- vs. Gilbert et al. [[@gilbert_comment_2016]](http://doi.org/10.1126/science.aad7243)
- Sharing [data](https://osf.io/ezcuj/wiki/home/?_ga=1.260625677.1251838540.1458403228) focuses attention on substantive issues

@@

<div class="centered">
<a href="http://doi.org/10.1126/science.1093567">
<img src="img/deloache.science.jpg" height=400px>
</a>

[[@deloache_scale_2004]](http://doi.org/10.1126/science.1093567)
</div>

## Children's Scale Errors {.vcenter}
